ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-06-06 pyked.tex
Update with BY license and PDF metadata

% !TEX option = -shell-escape
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{icck}

@@

@@

\usepackage{microtype}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
%======================================================================

@@

\author[1]{Bryan W.~Weber}
\author[2]{Kyle E.~Niemeyer\thanks{Corresponding author: \email{kyle.niemeyer@oregonstate.edu}}}

\affil[1]{Department of Mechanical Engineering, University of Connecticut, Storrs, CT, USA}
\affil[2]{School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University, Corvallis, OR, USA}

@@

\begin{keyword}
    Chemical kinetics\sep Experimental data\sep Autoignition\sep Data standard \\
\end{keyword}

%====================================================================
\begin{abstract} % not to exceed 200 words
Fundamental experimental measurements of quantities including ignition delay times,
laminar flame speeds, and species profiles serve important roles in understanding
fuel chemistry and validating chemical kinetic models. However, despite both the
importance and abundance of such information in the literature, the community lacks
a widely adopted standard format for this data. This impedes both sharing and wide
use by the community. In this talk, we will introduce a new Chemical Kinetics
Experimental Data format, ChemKED, and the related Python-based package for creating
and validating ChemKED-formatted files called PyKED. We will also review past and
related efforts, and motivate the need for a new solution. ChemKED currently supports
the representation of autoignition delay time and laminar flame speed measurements.
ChemKED-formatted files contain all of the information needed to simulate experimental
data points, including the uncertainty of the data. ChemKED is based on the YAML data
serialization language, and is intended as a human- and machine-readable standard for
easy creation and automated use.
Development of ChemKED and PyKED occurs openly on GitHub under the
BSD 3-clause license, and contributions from the community are welcome. Plans for
future development include support for experimental data from jet stirred reactor,
extinction, and speciation measurements.
\end{abstract}

>>>>

% !TEX option = -shell-escape
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ussci}

@@

\usepackage{xmpincl}
\includexmp{CC_Attribution_4.0_International}

\hypersetup{
    pdftitle={ChemKED: a human- and machine-readable data standard for chemical kinetics experiments},%
    pdfauthor={Bryan W. Weber},%
}

@@

\usepackage{microtype}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

\author[1*]{Bryan W. Weber}
\author[2]{Kyle E. Niemeyer}

\affil[1]{Department of Mechanical Engineering, University of Connecticut, Storrs, CT, USA}
\affil[2]{School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University, Corvallis, OR, USA}
\affil[*]{Corresponding author: \email{bryan.weber@uconn.edu}}

@@

%====================================================================
\begin{abstract} % not to exceed 200 words
Fundamental experimental measurements of quantities including ignition delay
times, laminar flame speeds, and species profiles serve important roles in
understanding fuel chemistry and validating chemical kinetic models. However,
despite both the importance and abundance of such information in the literature,
the community lacks a widely adopted standard format for this data. This impedes
both sharing and wide use by the community. In this paper, we will introduce a
new Chemical Kinetics Experimental Data format, ChemKED, and the related
Python-based package for creating and validating ChemKED-formatted files called
PyKED. We will also review past and related efforts, and motivate the need for a
new solution. ChemKED currently supports the representation of autoignition
delay time and laminar flame speed measurements. ChemKED-formatted files contain
all of the information needed to simulate experimental data points, including
uncertainty. ChemKED is based on the YAML data serialization language, and is
intended as a human- and machine-readable standard for easy creation and
automated use. Development of ChemKED and PyKED occurs openly on GitHub under
the BSD 3-clause license, and contributions from the community are welcome.
Plans for future development include support for experimental data from jet
stirred reactor, extinction, and speciation measurements.
\end{abstract}

% (Provide 2-4 keywords describing your research. Only abbreviations firmly
% established in the field may be used. These keywords will be used for
% sessioning/indexing purposes.)
\begin{keyword}
    chemical kinetics\sep data standard\sep software\sep database
\end{keyword}
